---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# managecrownsdata <a href="https://hugolblc.github.io/managecrownsdata/">

<!-- badges: start -->
<!-- badges: end -->

This R package aims at streamlining, standardizing and facilitating processing of repetead UAV surveys from R. It focuses (for now) on RGB data. It notably allows generating 3D and 4D mosaics & mosaics spatial alignment using state-of-the-art approaches,  provides tools to generate reference labels, segment crowns (?) and classify crown phenophases.

## Pre-installation (called once)

```{r, eval=FALSE}

# Install anaconda 'https://www.anaconda.com/'

#Install reticulate 
install.packages('reticulate')

#Install miniconda
library(reticulate)
options(timeout=100000000) 
install_miniconda()

# Create a conda environment from the environment.yaml file
conda_create(envname = "pipeline_test_R",
             environment = 'C:/Users/2022hl001/Downloads/environment.yaml')

```

## Install package

You can install the development version of managecrownsdata like so:

```{r, eval=FALSE}
remotes::install_github("hugolblc/managecrownsdata")
```

## Use managecrownsdata (called before loading `managecrownsdata` )

```{r, eval=FALSE}
# Restrt R session
.rs.restartR()

# Set environment
Sys.setenv(RETICULATE_PYTHON= reticulate::conda_python('pipeline_test_R'))

library(reticulate)

use_condaenv(condaenv = "pipeline_test_R", required = TRUE)

```


## Getting Started

```{r, eval=FALSE}
library(managecrownsdata)

arosics_in_r(path_in = 'E:/test_arosics/in', 
             ref_filepath = 'E:/test_arosics/ref/CHM_1m_crs2.tif',
             out_dir_path = 'E:/test_arosics/out')
```
